State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-15 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Edits to Section 10 on Recommendations

We provide specific recommendations for future consideration -- these are not
criticisms of past and/or current development practices. We expand on some of
the ideas from our interviews, and bring in further ideas that could have a
noticeable impact. The ``new'' ideas are not novel to this paper but rather from
the software engineering and software carpentry domains, but have not yet seen
wide adoption.  We list the ideas roughly in the order of increasing
implementation effort.

@@

Continuous integration involves building and testing the software every
time a coherent change is made to the code (i.e. via a Pull Request)%
\cite[p.\ 13] {HumbleAndFarley2010}, \cite{ShahinEtAl2017, Fowler2006}. Initial
setup can be cumbersome, but
the benefits are impressive:
\begin{itemize}
    \item Elimination of headaches associated with a separate integration phase
    \cite{Fowler2006}, \cite[p.\ 20]{HumbleAndFarley2010}.
    \item Detection and removal of bugs \cite{Fowler2006} via
    automated testing.  
    \item Everyone is always working on a stable base that always passes all
    the tests.
    \item If the CI system uses generators and linters, it will also have
    current documentation and clean code.
\end{itemize}

@@

Multiple pain points, especially technology hurdles
(\ppref{P_TechnologyHurdles}), could be alleviated by moving to a web
application. However, this must be an active decision as it may not be a good
fit in all cases.  The decision needs to be based on whether, on balance, this
would improve the four factors identified earlier: compatibility,
maintainability, performance, and security. The following considerations may
help a team make a decision about the move to web applications:

@@

\item \textbf{Modern technologies may improve frontend performance.} 
Complex, graphics-heavy user-interfaces often do not respond as quickly
as native applications.  However, new technologies may help. For example,
some JavaScript libraries can help the frontend harness the power of the
computer's GPU and accelerate graphical computing. In addition, there are new
frameworks helping developers with cross-platform compatibility. For example,
the \href{https://flutter.dev/}{Flutter} project enables support for web,
mobile, and desktop OS with one codebase.  Other options include
\href{https://vuejs.org/} {Vue}, \href{https://angular.io/} {Angular} and
\href{https://reactjs.org/} {React}, and \href{https://elm-lang.org/}{Elm}.

@@

%JC: I'm aware of too many caveats wrt this recommendation, so I am taking
% it out.
%SS: okay, I agree.
%
%\item \textbf{Remove privacy from sensitive data.} For data with sensitive
%information, a team can ask the data owner to remove such information or add
%noise to protect privacy. One example is using de-identified copies of medical
%images for testing.

@@

Rigorous inspection finds 60-65\% of latent defects on
average, and often tops 85\% in defect removal efficiency \cite{Jones2008}. The
success rate of code inspection is generally higher than most forms of testing,
which average between 30 --- 35\% for defect removal efficiency
\cite{EbertAndJones2009, Jones2008}. For research software, Kelly and Shepard
\cite{KellyAndShepard2000} show a task based inspection approach can be
effective.

Due to improving code quality and increasing knowledge transfer, peer review
addresses the same pain points and qualities as linters \ppref{P_LackDevTime},
\qref{Q_Maintainability} and \ppref{P_Correctness}. The benefits can be
increased by extending reviews to all artifacts, including documentation, build
scripts, test cases and the development process itself.

>>>>

We provide specific recommendations for future consideration -- these are not
criticisms of past and/or current development practices. We expand on some of
the ideas from our interviews, and bring in further ideas that could have a
noticeable impact. The ``new'' ideas are not novel to this paper but rather from
the software engineering and software carpentry domains, but these ideas have
not yet seen wide adoption for MI software.  We list the ideas roughly in the
order of increasing implementation effort.

@@

Continuous integration involves building and testing the software every time a
coherent change is made to the code (i.e.\ via a pull request)~\cite[p.\ 13]
{HumbleAndFarley2010}, \cite{ShahinEtAl2017, Fowler2006}. Initial setup can be
cumbersome, but the benefits are impressive:

\begin{itemize}
    \item Elimination of headaches associated with a separate integration phase
    \cite{Fowler2006}, \cite[p.\ 20]{HumbleAndFarley2010}.
    \item Detection and removal of bugs \cite{Fowler2006} via
    automated testing.  
    \item Everyone is always working on a stable base that always passes all tests.
    \item If the CI system uses generators and linters, it will also have
    current documentation and clean code.
\end{itemize}

@@

Multiple pain points, especially technology hurdles
(\ppref{P_TechnologyHurdles}), could be alleviated by moving to a web
application. However, this must be an active decision as it may not be a good
fit in all cases.  The decision needs to be based on whether, on balance, this
would improve the four factors identified earlier for the technology hurdle:
compatibility, maintainability, performance, and security. The following
considerations may help a team make a decision about the move to web
applications:

@@

\item \textbf{Modern technologies may improve frontend performance.} 
Complex, graphics-heavy user-interfaces often do not respond as quickly
as native applications.  However, new technologies may help. For example,
some JavaScript libraries can help the frontend harness the power of the
computer's GPU and accelerate graphical computing. In addition, there are new
frameworks helping developers with cross-platform compatibility. For example,
the \href{https://flutter.dev/}{Flutter} project supports web,
mobile, and desktop OS with one codebase.  Other options include
\href{https://vuejs.org/} {Vue}, \href{https://angular.io/} {Angular},
\href{https://reactjs.org/} {React}, and \href{https://elm-lang.org/}{Elm}.

@@

%JC: I'm aware of too many caveats wrt this recommendation, so I am taking
% it out.
%SS: I agree with the removal.
%
%\item \textbf{Remove privacy from sensitive data.} For data with sensitive
%information, a team can ask the data owner to remove such information or add
%noise to protect privacy. One example is using de-identified copies of medical
%images for testing.

@@

Rigorous inspection finds 60--65\% of latent defects on
average, and often tops 85\% in defect removal efficiency \cite{Jones2008}. The
success rate of code inspection is generally higher than most forms of testing,
which average between 30--35\% for defect removal efficiency
\cite{EbertAndJones2009, Jones2008}. For research software, Kelly and Shepard
\cite{KellyAndShepard2000} show a task based inspection approach can be
effective.

Due to improving code quality and increasing knowledge transfer, peer review
addresses the same pain points and qualities as linters (\ppref{P_LackDevTime},
\qref{Q_Maintainability} and \ppref{P_Correctness}). The benefits can be
increased by extending reviews to all artifacts, including documentation, build
scripts, test cases and the development process itself.
